The Accuracy of KNN, decision tree, random forest, SVM, neural network, naive Bayes classifier and PLA for early Prediction of Diabetes

### 2023-04-05 hw1/paper/main.tex
merge NN

  To find out which techniques is more suitable to predict diabetes, this work examines the diagnosis of diabetes 
  using KNN algorithm, decision tree, random forest, SVM, neural network naive Bayes classifier, and PLA.
\section{Related works}
\label{sec:Related works}
  \bf{k-nearest neighbors (KNN) classification algorithm}: \rm{The} KNN classification algorithm is a supervised learning 
  method which is first developed by Fix and Hodges \cite{10.2307/1403797}. The idea of KNN is based on the idiom, 
  "birds of a feather flock together". By picking the $k$-nearest neighbors of a data point, the unkonwn class label 
  can be determined. Lots of works \cite{6528591} \cite{8276012} \cite{vijayan2014study} show the fact that KNN performs  
  well for prediction of diabetes disease.

@@

  \bf{neural network}: \rm{Neural} network have been used in many fields to deal with intricate datas.With input layer, hidden layer and output layer constructed by neurons, each data in dataset is processed while passing through neurons, layer by layer.After the processing, the outcome can be used to predict.Using back propogation, the accuracy of predictions increase in each training.In order to construct the hidden layer more efficient, NAS(Neural Arcitecture Searching) is used to search suitable structure for hidden layer, increasing the accuracy.According to \cite{Gadekallu2020}\cite{Beghriche2021}, many neural network have been constructed and trained already, with high efficiency and accuracy in prediction of diabetes.

@@

\section{Naive Bayes classifier}
  First, let's explain the princple of Naive Bayes classifier, here is a very intuitive and easy-to-understand example, consider 
  you are a scientist who study earthquake, what a intresting relation attract you is when there are eqrthquake, the number of 
  rainy days is particular high while its low when there are no earthquake. Although it may sounds nonsense, we can assume there 
  may exists a positive relation betweeen earthquake and rainy days. Here we talk about the Bayesian theorem, which is the basis 
  of naive Bayes classifier. What the formula it give is $P(A|B) = \frac{P(A\capB)}{P(B)}$. Consider we need to predict the result 
  by the data meaning the outcome will be unknown, what we need do is just change the formula a little bit and it becomes: $P(A|B) = \frac{P(B|A)*P(A)}{P(B)}$. 
  We can consider $A$ as the outcome and $B$ as data. Given a data that contains a sequence of data and various outcomes. We just 
  record each event in each dimension and compute their conditional probabilities for each outcome and store these result in other 
  place. When predicting the outcome using given data, find the conditional probability of each event in given data for one outcome 
  and multiply them. Keep repeating until we had computed all conditional probability for each outcome, then find the maximum one, 
  which is the most likely outcome. The problem is, when given is a continuous value instead of individual events, it look like we 
  need to partition this continuous interval as individual events. However, the difficulty is how to find the best partition that 
  can fit the model best. What I use to slove this problem is gene alogrithm. First ecord maximum and minimum values of given data 
  in each dimension. Step2 is randomly partition data in each dimension according the maximum and minimum value we record before 
  and repeat 100 times to generate enoguh species. Step3 is test the accuracy of the model on the training data and keep top 15 
  good species and kill the rest. Step4 is let the these elite to crossover, which means let them pass their partition to kids. 
  Step4 is when there is enough offspring, all offspring will start mutation, which means their partitions will slightly shift, 
  merge, split, or disapar etc..., make each animal different to optmize the model. And back to step2, here I called an evolution. 
  We thus find the partition that is close to optimal solution after enough evolution.

>>>>

  To find out which techniques is more suitable to predict diabetes, this work examines the diagnosis of diabetes 
  using KNN algorithm, decision tree, random forest, SVM, neural network naive Bayes classifier, and PLA.
\section{Related works}
\label{sec:Related works}

  \bf{k-nearest neighbors (KNN) classification algorithm}: \rm{The} KNN classification algorithm is a supervised learning 
  method which is first developed by Fix and Hodges \cite{10.2307/1403797}. The idea of KNN is based on the idiom, 
  "birds of a feather flock together". By picking the $k$-nearest neighbors of a data point, the unkonwn class label 
  can be determined. Lots of works \cite{6528591} \cite{8276012} \cite{vijayan2014study} show the fact that KNN performs  
  well for prediction of diabetes disease.

@@

  \bf{neural network}: \rm{Neural} network have been used in many fields to deal with intricate datas.With input layer, hidden 
  layer and output layer constructed by neurons, each data in dataset is processed while passing through neurons, layer by layer. 
  After the processing, the outcome can be used to predict.Using back propogation, the accuracy of predictions increase in each 
  training. In order to construct the hidden layer more efficient, NAS(Neural Arcitecture Searching) is used to search suitable 
  structure for hidden layer, increasing the accuracy.According to \cite{Gadekallu2020}\cite{Beghriche2021}, many neural network 
  have been constructed and trained already, with high efficiency and accuracy in prediction of diabetes.

@@

\section{Naive Bayes classifier}
  First, let's explain the princple of Naive Bayes classifier, here is a very intuitive and easy-to-understand example, consider 
  you are a scientist who study earthquake, what a intresting relation attract you is when there are eqrthquake, the number of 
  rainy days is particular high while its low when there are no earthquake. Although it may sounds nonsense, we can assume there 
  may exists a positive relation betweeen earthquake and rainy days. Here we talk about the Bayesian theorem, which is the basis 
  of naive Bayes classifier. What the formula it give is $P(A\mid B) = \frac{P(A\cap B)}{P(B)}$. Consider we need to predict the result 
  by the data meaning the outcome will be unknown, what we need do is just change the formula a little bit and it becomes: $P(A\mid B) = \frac{P(B\mid A)\cdot P(A)}{P(B)}$ 
  We can consider $A$ as the outcome and $B$ as data. Given a data that contains a sequence of data and various outcomes. We just 
  record each event in each dimension and compute their conditional probabilities for each outcome and store these result in other 
  place. When predicting the outcome using given data, find the conditional probability of each event in given data for one outcome 
  and multiply them. Keep repeating until we had computed all conditional probability for each outcome, then find the maximum one, 
  which is the most likely outcome. The problem is, when given is a continuous value instead of individual events, it look like we 
  need to partition this continuous interval as individual events. However, the difficulty is how to find the best partition that 
  can fit the model best. What I use to slove this problem is gene alogrithm. First ecord maximum and minimum values of given data 
  in each dimension. Step2 is randomly partition data in each dimension according the maximum and minimum value we record before 
  and repeat 100 times to generate enoguh species. Step3 is test the accuracy of the model on the training data and keep top 15 
  good species and kill the rest. Step4 is let the these elite to crossover, which means let them pass their partition to kids. 
  Step4 is when there is enough offspring, all offspring will start mutation, which means their partitions will slightly shift, 
  merge, split, or disapar etc..., make each animal different to optmize the model. And back to step2, here I called an evolution. 
  We thus find the partition that is close to optimal solution after enough evolution.
